Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-03-30 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

\textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as negative pairs.
\textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, which encourages the model to produce similar representations for positive pairs and dissimilar representations for negative pairs.
\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or music similarity, both in the symbolic and time domains.
\subsubsection{Strengths}

CSSL inherits the strengths of both SSL and CLMR:

\begin{enumerate}
\item Reduces dependency on labeled data: By leveraging inductive bias and the structure of musical data, CSSL can learn from large amounts of unlabeled data.
\item Encourages feature extraction: CSSL promotes learning useful and discriminative features or representations
\end{enumerate}

\section{}

We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}. Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining.

>>>>

\begin{enumerate}
\item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, which encourages the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
\item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or music similarity, both in the symbolic and time domains.
\end{enumerate}

\subsubsection{Strengths}

CSSLMR inherits the strengths of both SSL and CLMR:

\begin{enumerate}
\item Reduces dependency on labeled data: by leveraging inductive bias (assuming a known invariance across the data samples), CSSL can learn from large amounts of unlabeled data.
\item Encourages feature extraction: CSSLMR promotes learning useful and discriminative features or representations
\end{enumerate}

\section{Model architecture}

We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}. Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.
